BERT Model Compression and Weight Sharing

### 2019-05-12 paper/paper.tex
Testing code
Add introduction and result tables

\documentclass[11pt]{article}

@@

Example Structure:
\begin{itemize}
\item What is the problem of interest and what (high-level) are the current best methods for solving it?
\item How do you plan to improve/understand/modify this or related methods?
\item Preview your research process, list the contributions you made, and summarize your experimental findings.
\end{itemize}

@@

Deep Neurel Networks (DNNs) have become extremely large in size with growing
complexities. A BERT base model has 110M parameters and takes 438 MB disk space
to store. This makes it very hard to deploy those models on mobile devices,
which in most cases have limited storage and RAM and lower computational
resources. As a result, we are not able to store multiple models for different
tasks on mobile devices, and evaluating one single model also takes too much
time due to computational capacity limit. The challenge that we are facing is
how to compress DNNs in size while keeping their predictive performance
competitive with full model.

@@

% \begin{table}
%   \centering
%   \missingfigure[figheight=5cm]{}
%   \caption{Secondary table or figure in results section.}
%   \label{fig:mainres}
% \end{table}

>>>>

\documentclass[10pt]{article}

@@

% Example Structure:
% \begin{itemize}
% \item What is the problem of interest and what (high-level) are the current best methods for solving it?
% \item How do you plan to improve/understand/modify this or related methods?
% \item Preview your research process, list the contributions you made, and summarize your experimental findings.
% \end{itemize}

Deep Neurel Networks (DDNs) have evolved to the state-of-art for many tasks in
language modeling. In the meantime, they have become increasingly large in
size, due to both pre-trained embeddings and deeper networks. However, in
order to deploy the models on more resource-conscious devices efficiently,
such as mobile devices or even older personal laptops, as opposed to on cloud
virtual machines, it is crucial to reduce the size of the models.

Previous work has had a lot of success in computer vision tasks.
\citet{han2015deep} was able to reduce the size of AlexNet by 35$\times$ and
the size of VGG-16 by 49$\times$ without loss of accuracy. Recently, similar
compression techniques were applied by \citet{cheong2014transformer} on
Transformers and reduced the size by a factor of 5.85 while retaining 98.43\%
of the performance. To the best of our knowledge, compressing language models
remains an under-studied field.

In this paper, we proved that DeepTwist framework works well on compressing
language models with pruning. {\color{red} TODO: prune99 result}.

proposed weight-sharing method Difference Pruning

attempt kd but does not work well

@@

DNNs have become extremely large in size with growing complexities. A BERT
base model has 110M parameters and takes 438 MB disk space to store. This
makes it very hard to deploy those models on mobile devices, which in most
cases have limited storage and RAM and low computational resources. As a
result, we are not able to store multiple models for different tasks on mobile
devices. Allocating hundreds of megabytes to to those models is also not
realistic for mobile apps such as Gmail or Facebook. And due to increasing
privacy concerns, users prefer models generating predictions based on their
input to be running locally instead of sending information to the cloud. Last
but not least, evaluating enormous models takes too much time on mobile
devices and can drain batteries significantly.

The challenge that we are facing is therefore how to compress DNNs in size
while keeping their predictive performance competitive with full model.

% Though these neural networks are very powerful, the
% large number of weights consumes considerable storage and memory bandwidth. For example, the AlexNet Caffemodel is over 200MB, and the VGG-16 Caffemodel is over 500MB (BVLC). This makes it difficult to deploy deep neural networks on mobile system.
% First, for many mobile-first companies such as Baidu and Facebook, various apps are updated via different app stores, and they are very sensitive to the size of the binary files. For example, App Store has the restriction “apps above 100 MB will not download until you connect to Wi-Fi”. As a result, a feature that increases the binary size by 100MB will receive much more scrutiny than one that increases it by 10MB. Although having deep neural networks running on mobile has many great

@@

\begin{table}[tbh]
        \caption{Results for DeepTwist}
        \label{tab:deeptwist_results}
        \centering
        \vspace{1em}
        \begin{tabular}{lccccc}
\toprule
{} &               type &  param &  val loss &   val acc \\
{} & 
\hypertarget{tabcol:1}{(1)} & \hypertarget{tabcol:2}{(2)} & \hypertarget{tabcol:3}{(3)} & \hypertarget{tabcol:4}{(4)} \\ \midrule
0  &  diff prune global &   $90$ &   $0.211$ &   $0.912$ \\
1  &              prune &   $20$ &   $0.291$ &   $0.886$ \\
2  &              prune &   $80$ &   $0.532$ &   $0.767$ \\
3  &         diff prune &   $80$ &   $0.222$ &   $0.916$ \\
4  &  diff prune global &   $99$ &       --- &       --- \\
5  &  diff prune global &   $90$ &   $0.213$ &   $0.916$ \\
6  &         diff prune &   $40$ &   $0.203$ &   $0.909$ \\
7  &                svd &   $50$ &   $0.490$ &   $0.810$ \\
8  &                svd &  $200$ &   $0.459$ &   $0.845$ \\
9  &              prune &   $40$ &   $0.424$ &   $0.845$ \\
10 &              prune &   $60$ &   $0.425$ &   $0.815$ \\
11 &  diff prune global &   $99$ &   $0.230$ &   $0.901$ \\
12 &  diff prune global &   $99$ &   $0.222$ &   $0.905$ \\
13 &         diff prune &   $99$ &   $0.222$ &   $0.913$ \\
14 &         diff prune &   $95$ &   $0.221$ &   $0.916$ \\
15 &         diff prune &   $90$ &   $0.216$ &   $0.916$ \\
16 &         diff prune &   $60$ &   $0.209$ &   $0.920$ \\
17 &                svd &  $100$ &   $0.515$ &   $0.823$ \\
18 &                svd &  $150$ &   $0.456$ &   $0.828$ \\
19 &         diff prune &   $80$ &   $2.533$ &   $0.491$ \\
20 &         diff prune &   $90$ &       --- &       --- \\
21 &  diff prune global &    $0$ &   $0.738$ &   $0.509$ \\
22 &         diff prune &    $0$ &   $0.692$ &   $0.522$ \\
23 &         diff prune &    $0$ &   $1.854$ &   $0.491$ \\
\bottomrule
\end{tabular}

\end{table}

\begin{table}[tbh]
        \caption{Results for Knowledge Distillation}
        \label{tab:kd_results}
        \centering
        \vspace{1em}
        \begin{tabular}{lccccccc}
\toprule
{} &  framework &  type &  val loss &  ß val acc \\
{} & \hypertarget{tabcol:1}{(1)} & \hypertarget{tabcol:2}{(2)} & \hypertarget{tabcol:3}{(3)} & \hypertarget{tabcol:4}{(4)} \\
\midrule
0 &        nokd &   CNN &   $0.906$ &   $0.799$ \\
1 &        nokd &   CNN &   $0.448$ &   $0.784$ \\
2 &        nokd &   CNN &   $0.856$ &   $0.812$ \\
3 &          kd &  LSTM &   $0.738$ &   $0.831$ \\
4 &          kd &   CNN &   $0.423$ &   $0.834$ \\
\bottomrule
\end{tabular}

\end{table}
